
## System Prep
## Load current elo ratings

```{r echo=FALSE}
library(dplyr); library(data.table); library(sqldf)

```

## Create raw PBP

```{r echo=FALSE}

read_raw_pbp <- function(file_year) {
  
  raw_pbp <- read.csv(paste0("~/Documents/CWA/HockeyScrape/nhl_pbp",file_year,".csv")) %>%
          mutate(season = file_year) %>%
          select(-ends_with("X"), -starts_with("Unnam"))
          
  return(raw_pbp)

}

read_raw_shift <- function(file_year) {
  
  raw_shift <- read.csv(paste0("~/Documents/CWA/HockeyScrape/nhl_shifts",file_year,".csv")) %>%
          mutate(season = file_year,
                 Team = ifelse(Team == "SJS","S.J",
                        ifelse(Team == "TBL","T.B",
                        ifelse(Team == "LAK","L.A",
                        ifelse(Team == "NJD","N.J",
                               as.character(Team)))))) %>%
          select(-ends_with("X"), -ends_with("Date"), -starts_with("Unnam")) %>%
          mutate(Game_Id = ifelse(nchar(Game_Id) > 6, as.integer(substr(Game_Id,6,11)), as.integer(Game_Id)))
  
  return(raw_shift)

}

read_xG_scored <- function(file_year) {
  
  xG_data <- read.csv(paste0("~/Documents/CWA/HockeyScrape/scored_data",file_year,".csv")) %>%
          select(-ends_with("X"), -ends_with("Date")) %>%
          mutate(Game_Id = ifelse(nchar(Game_Id) > 6, as.integer(substr(Game_Id,6,11)), as.integer(Game_Id)),
                 xG = xG_raw,
                 xG_team = ifelse(is_Rebound == 0, xG_raw,
                          ifelse(is_Rebound == 1 & lag(is_Rebound) == 0, xG_raw * (1-lag(xG_raw)),
                                 ifelse(is_Rebound == 1 & lag(is_Rebound) == 1 & lag(is_Rebound,2) == 0,
                                        xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)),
                                        ifelse(is_Rebound == 1 & lag(is_Rebound) == 1 & lag(is_Rebound,2) == 1 & lag(is_Rebound,3) == 0,
                                               xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)) * (1-lag(xG_raw,3)),
                                               ifelse(is_Rebound == 1 & lag(is_Rebound) == 1 & lag(is_Rebound,2) == 1 & lag(is_Rebound,3) == 1 & lag(is_Rebound,4) == 0,
                                                      xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)) * (1-lag(xG_raw,3)) * (1-lag(xG_raw,4)),
                                                      xG_raw * (1-lag(xG_raw)) * (1-lag(xG_raw,2)) * (1-lag(xG_raw,3)) * (1-lag(xG_raw,4))))))))

  return(xG_data)

}



seasons <- c(seq(20142015,20172018,by=10001))

pbp_all_raw <- do.call(dplyr::bind_rows,lapply(FUN=read_raw_pbp,seasons))

shift_all_raw <- do.call(dplyr::bind_rows,lapply(FUN=read_raw_shift,seasons))

season_blocks <- c('2015_2016','2017_2018')

scored_data <- do.call(dplyr::bind_rows,lapply(FUN=read_xG_scored,season_blocks))

i = 8477497

sm_shifts_games <- shift_all_raw %>% filter(Player_Id == i & season == "20172018") %>%
  group_by(Game_Id) %>% summarise(games = n_distinct(Game_Id), TOI = sum(Duration)/60)

print("Done")
```

## Load Scored Data and Create Master PBP

```{r echo=FALSE}

### Join xG to all PBP data
player_onice_data <- pbp_all_raw %>% 
            select(-c(xC, yC, Description)) %>% ## drop some duplicates
            unique() %>%
  mutate(Event = ifelse(Event %in% c("GIVE","TAKE"),"TURN",as.character(Event)),
         Type = ifelse(Type %in% c("DEFLECTED","TIP-IN"),"DEFLECTED",
                       ifelse(Type %in% c("WRIST SHOT","SNAP SHOT","WRAP-AROUND"),"WRIST SHOT",as.character(Type)))) %>%
         
  left_join(unique(scored_data[c("season", "Game_Id", "Period","Seconds_Elapsed", "Event","Type", "xG", "xG_team")]), by = c("season","Game_Id","Period","Seconds_Elapsed","Event","Type")) %>%
  mutate(season = as.factor(season),
         Goal = ifelse(Event=="GOAL",1,0),
         xG = ifelse(is.na(xG),0,as.numeric(xG)),
         xG_team = ifelse(is.na(xG_team),0,as.numeric(xG_team)),
         ## Duration
         Same_Period = ifelse(Game_Id == lag(Game_Id) & Period == lag(Period), 1, 0),                    
         Duration = ifelse(Same_Period == 1, Seconds_Elapsed - lag(Seconds_Elapsed), 0) ) %>%
  # Remove Regular Season Shootouts
  filter(!(Period== "5" & substr(Game_Id,1,1) == "2")) %>%
  #filter(!Event %in% c("PGSTR","PGEND","ANTHEM")) %>%
  mutate(event_index = row_number())
  
### Standardize Player Names
player_names <- player_onice_data  %>%
   select(starts_with("homePlayer"), starts_with("awayPlayer"), Away_Goalie,Away_Goalie_Id,Home_Goalie,Home_Goalie_Id, p1_name, p2_name, p3_name,p1_ID, p2_ID, p3_ID, season) 


player_onice_data_standard <- player_onice_data  %>%
              filter(Ev_Team != "") %>%
              distinct() %>%
              mutate(season = as.numeric(as.character(season)),
                     Game_Id = as.numeric(Game_Id),
                     seconds_elapsed = ((Period - 1) * 1200 ) + Seconds_Elapsed) %>% 
              select(event_index, season, Game_Id, Date, Ev_Team, Home_Zone, Event, xG_team, xG, Home_Coach, Away_Coach, Strength, Away_Players, Home_Players, seconds_elapsed, p1_ID, p2_ID, p3_ID) 
              

GM_EVENTS <- player_onice_data_standard %>% filter(season == "20172018" & Game_Id == 20050)

```


## Find Unique Skaters

```{r}

goalie_id_list <- as.data.frame(rbind(distinct(player_names[c(25:26,35)]) %>% rename(Goalie = Away_Goalie, goalieID = Away_Goalie_Id),
                           distinct(player_names[c(27:28,35)]) %>% rename(Goalie = Home_Goalie, goalieID = Home_Goalie_Id))) %>% 
              na.omit() %>%
              group_by(goalieID, Goalie) %>%
              mutate(cnt = n()) %>%
              arrange(-cnt) %>%
              group_by(goalieID) %>%
              mutate(Goalie = ifelse(cnt == max(cnt),as.character(Goalie),NA)) %>%
              tidyr::fill(Goalie) %>%
              distinct() %>%
              select(-c(cnt))


skater_id_list <- as.data.frame(rbind(
       distinct(player_names[c(1:2,35)]) %>% rename(Player = homePlayer1, shooterID = homePlayer1_id) %>% mutate(Pos2 = 1),
       distinct(player_names[c(3:4,35)]) %>% rename(Player = homePlayer2, shooterID = homePlayer2_id) %>% mutate(Pos2 = 2),
       distinct(player_names[c(5:6,35)]) %>% rename(Player = homePlayer3, shooterID = homePlayer3_id) %>% mutate(Pos2 = 3),
       distinct(player_names[c(7:8,35)]) %>% rename(Player = homePlayer4, shooterID = homePlayer4_id) %>% mutate(Pos2 = 4),
       distinct(player_names[c(9:10,35)]) %>% rename(Player = homePlayer5, shooterID = homePlayer5_id) %>% mutate(Pos2 = 5),
       distinct(player_names[c(11:12,35)]) %>% rename(Player = homePlayer6, shooterID = homePlayer6_id) %>% mutate(Pos2 = 6),
       distinct(player_names[c(13:14,35)]) %>% rename(Player = awayPlayer1, shooterID = awayPlayer1_id) %>% mutate(Pos2 = 1),
       distinct(player_names[c(15:16,35)]) %>% rename(Player = awayPlayer2, shooterID = awayPlayer2_id) %>% mutate(Pos2 = 2),
       distinct(player_names[c(17:18,35)]) %>% rename(Player = awayPlayer3, shooterID = awayPlayer3_id) %>% mutate(Pos2 = 3),
       distinct(player_names[c(19:20,35)]) %>% rename(Player = awayPlayer4, shooterID = awayPlayer4_id) %>% mutate(Pos2 = 4),
       distinct(player_names[c(21:22,35)]) %>% rename(Player = awayPlayer5, shooterID = awayPlayer5_id) %>% mutate(Pos2 = 5),
       distinct(player_names[c(23:24,35)]) %>% rename(Player = awayPlayer6, shooterID = awayPlayer6_id) %>% mutate(Pos2 = 6)
                           )) %>% 
              na.omit() %>%
              #
              group_by(shooterID, Player) %>%
              mutate(cnt = n(),
                     Pos_Spot = mean(Pos2, na.rm=T)) %>%
              arrange(-cnt) %>%
              group_by(shooterID) %>%
              mutate(Player = ifelse(cnt == max(cnt),as.character(Player),NA)) %>%
              tidyr::fill(Player) %>%
              select(-c(cnt, Pos2)) %>%
              distinct() %>%
              anti_join(goalie_id_list, by = c("shooterID" = "goalieID"))

```

### Shift Data

```{r}

schedule <- pbp_all_raw %>% select(season, Game_Id, Home_Team, Away_Team) %>% distinct()

season_toi_function <- function(szn) {

  game_toi_function <- function(game) {
    
      print(paste0(szn, game))
      skater_game_df <- shift_data %>% filter(Game_Id == game) %>% 
                inner_join(schedule, by = c("season","Game_Id"))
      
      rows = skater_game_df %>%
            summarise(Game_End = max(seconds_elapsed)) %>%
            mutate(Game_End = ifelse(Game_End > 3900 & game < 30000,3900,Game_End))
      
      game_events <- player_onice_data_standard %>% 
                filter(season == szn & Game_Id == game) %>%
                  group_by() %>%
                  mutate(Home_Coach = max(Home_Coach, na.rm = T),
                         Away_Coach = max(Away_Coach, na.rm = T),
                         Date = max(Date, na.rm = T),
                         season = max(season, na.rm = T),
                         stoppage = ifelse(Event == "GOAL" | (lead(Event) == "FAC"), 1, 0),
                         
                         seconds_clean = ifelse(seconds_elapsed == lead(seconds_elapsed), seconds_elapsed - 0.5,
                                 ifelse(seconds_elapsed == lag(seconds_elapsed),seconds_elapsed + 0.5, seconds_elapsed))) 
      
      game_seconds <- data.frame(Game_Id = game, matrix(, nrow=max(rows$Game_End,3600) + 1, ncol=0)) %>%
                  mutate(seconds_elapsed = row_number() - 1) %>%
                  left_join(game_events %>% select(seconds_elapsed, stoppage), by = c("seconds_elapsed")) %>%
                  group_by(seconds_elapsed) %>%
                  summarise(stoppage = sum(stoppage)) %>%
                  mutate(game_start = ifelse(seconds_elapsed == min(seconds_elapsed),1,0))
      
            
                         
      
      feature_list <- c("season", "Game_Id", "Period", "Home_Team", "Away_Team", "awayPlayer1_id", "awayPlayer2_id", "awayPlayer3_id", "awayPlayer4_id", "awayPlayer5_id", "awayPlayer6_id", "homePlayer1_id", "homePlayer2_id", "homePlayer3_id", "homePlayer4_id", "homePlayer5_id", "homePlayer6_id","Away_Goalie_Id", "Home_Goalie_Id","event_index", "Date", "Ev_Team", "Home_Zone", "Event", "xG_team", "xG", "Home_Coach", "Away_Coach","p1_ID","p2_ID","p3_ID")

      game_df_long <- sqldf::sqldf("
                        SELECT b.season, Game_Id, a.seconds_elapsed, Period, b.Player, Player_Id, Start, End, Duration,
                                    CASE WHEN Home_Team == Team AND c.goalieID IS NOT NULL THEN 'Home_Goalie_Id' 
                                         WHEN Home_Team != Team AND c.goalieID IS NOT NULL THEN 'Away_Goalie_Id' 
                                         WHEN Home_Team == Team AND c.goalieID IS NULL THEN 'homePlayer' 
                                         WHEN Home_Team != Team AND c.goalieID IS NULL THEN 'awayPlayer' 
                                    ELSE '' END AS Player_Type, Team, Home_Team, Away_Team, Pos_Spot
                        FROM game_seconds as a
                        LEFT JOIN skater_game_df as b
                        ON ((b.Start < a.seconds_elapsed) OR (game_start = 1 AND b.Start = a.seconds_elapsed))
                        AND (a.seconds_elapsed <= b.End)
                        LEFT JOIN goalie_id_list as c
                        ON b.Player_Id = c.goalieID
                        AND b.season = c.season
                        LEFT JOIN skater_id_list as d
                        ON b.Player_Id = d.shooterID
                        AND b.season = d.season
                    ") %>%
        arrange(season, Game_Id, Period, seconds_elapsed, Player_Type, Pos_Spot, Duration, Start) %>%
        group_by(season, Game_Id, Period, seconds_elapsed, Player_Type) %>%
        mutate(Player_Type2 = ifelse(Player_Type %in% c("homePlayer","awayPlayer"), 
                                     paste0(Player_Type, row_number(),"_id"), 
                               ifelse(row_number() == 1, Player_Type, "NA_Goalie"))) %>%
        dcast(season + Game_Id + Period + seconds_elapsed + Home_Team + Away_Team ~ Player_Type2, value.var = "Player_Id") %>%
        ## Join Events data
        left_join(game_events, by = c("season", "Game_Id", "seconds_elapsed")) %>%
        mutate(second = ifelse(game_start != 1,1,0)) %>%
        group_by_at(vars(one_of(feature_list))) %>%
        summarise(Shift_Start = min(seconds_elapsed),
                  Shift_Duration = sum(second)) 
      
        #print(dim(game_df_long))
        return(game_df_long)
  }
  

  shift_data <-  read.csv(paste0("~/Documents/CWA/HockeyScrape/nhl_shifts",szn,".csv")) %>%
      mutate(seconds_elapsed = ((Period - 1) * 1200 ) + End,
             Start = ((Period - 1) * 1200 ) + Start,
             End = ((Period - 1) * 1200 ) + End,
             season = szn,
             Game_Id = ifelse(nchar(Game_Id) > 6, as.integer(substr(Game_Id,6,11)), as.integer(Game_Id)),
             Team = ifelse(Team == "SJS","S.J",
                        ifelse(Team == "TBL","T.B",
                        ifelse(Team == "LAK","L.A",
                        ifelse(Team == "NJD","N.J",
                               as.character(Team)))))) %>%
          select(-ends_with("X"), -ends_with("Date"), -starts_with("Unnam"))

  
  game_list <- shift_data %>% select(Game_Id) %>% distinct()
  
  game_toi_season <- do.call(dplyr::bind_rows,lapply(FUN=game_toi_function,game_list$Game_Id))

  return(game_toi_season)
    
}

#shift_data_15 <- season_toi_function(20142015)
#shift_data_16 <- season_toi_function(20152016)
#shift_data_17 <- season_toi_function(20162017)
shift_data_18 <- season_toi_function(20172018)

save(shift_data_15, file = "~/Documents/CWA/Hockey Data/shift_data_15.RData")
save(shift_data_16, file = "~/Documents/CWA/Hockey Data/shift_data_16.RData")
save(shift_data_17, file = "~/Documents/CWA/Hockey Data/shift_data_17.RData")
save(shift_data_18, file = "~/Documents/CWA/Hockey Data/shift_data_18.RData")

load("~/Documents/CWA/Hockey Data/shift_data_15.RData")
load("~/Documents/CWA/Hockey Data/shift_data_16.RData")
load("~/Documents/CWA/Hockey Data/shift_data_17.RData")
load("~/Documents/CWA/Hockey Data/shift_data_18.RData")

shift_data_all <- plyr::rbind.fill(shift_data_15,
                             shift_data_16,
                             shift_data_17,
                             shift_data_18)


#save(shift_data_all, file = "~/Documents/CWA/Hockey Data/shift_data_all.RData")


```


## Quality of Teammates/Competition

```{r}

load("~/Documents/CWA/Hockey Data/player_level_quality.RData")


skater_shift_onice_all <- shift_data_all %>%
  ungroup() %>%
  select(-c(Away_Goalie_Id,Home_Goalie_Id)) %>%
  mutate(season = as.character(season)) %>%
  ## H1
  left_join(player_level_quality, by = c("homePlayer1_id" = "shooterID", "season" = "season")) %>%
  rename(homePlayer1_elo = Predicted_CS, homePlayer1_Pos = Pos) %>%
  ## H2
  left_join(player_level_quality, by = c("homePlayer2_id" = "shooterID", "season" = "season")) %>%
  rename(homePlayer2_elo = Predicted_CS, homePlayer2_Pos = Pos) %>%
  ## H3
  left_join(player_level_quality, by = c("homePlayer3_id" = "shooterID", "season" = "season")) %>%
  rename(homePlayer3_elo = Predicted_CS, homePlayer3_Pos = Pos) %>%
  ## H4
  left_join(player_level_quality, by = c("homePlayer4_id" = "shooterID", "season" = "season")) %>%
  rename(homePlayer4_elo = Predicted_CS, homePlayer4_Pos = Pos) %>%
  ## H5
  left_join(player_level_quality, by = c("homePlayer5_id" = "shooterID", "season" = "season")) %>%
  rename(homePlayer5_elo = Predicted_CS, homePlayer5_Pos = Pos) %>%
  ## H6
  left_join(player_level_quality, by = c("homePlayer6_id" = "shooterID", "season" = "season")) %>%
  rename(homePlayer6_elo = Predicted_CS, homePlayer6_Pos = Pos) %>%
  ## A1
  left_join(player_level_quality, by = c("awayPlayer1_id" = "shooterID", "season" = "season")) %>%
  rename(awayPlayer1_elo = Predicted_CS, awayPlayer1_Pos = Pos) %>%
  ## A2
  left_join(player_level_quality, by = c("awayPlayer2_id" = "shooterID", "season" = "season")) %>%
  rename(awayPlayer2_elo = Predicted_CS, awayPlayer2_Pos = Pos) %>%
  ## A3
  left_join(player_level_quality, by = c("awayPlayer3_id" = "shooterID", "season" = "season")) %>%
  rename(awayPlayer3_elo = Predicted_CS, awayPlayer3_Pos = Pos) %>%
  ## A4
  left_join(player_level_quality, by = c("awayPlayer4_id" = "shooterID", "season" = "season")) %>%
  rename(awayPlayer4_elo = Predicted_CS, awayPlayer4_Pos = Pos) %>%
  ## A5
  left_join(player_level_quality, by = c("awayPlayer5_id" = "shooterID", "season" = "season")) %>%
  rename(awayPlayer5_elo = Predicted_CS, awayPlayer5_Pos = Pos) %>%
  ## A6
  left_join(player_level_quality, by = c("awayPlayer6_id" = "shooterID", "season" = "season")) %>%
  rename(awayPlayer6_elo = Predicted_CS, awayPlayer6_Pos = Pos) 

quality_onice_elos <- skater_shift_onice_all %>%
          select(ends_with("elo"),ends_with("Pos"))



```

## Clean Data with shift by shift elos  

```{r}

skater_onice_pos_clean <- skater_shift_onice_all %>%
       select(season, Game_Id, Period, Home_Team, Away_Team, Shift_Start, ends_with("_Pos")) %>%
       melt(id.vars = c("season", "Game_Id", "Period", "Home_Team", "Away_Team", "Shift_Start"), value.name = "pos") %>%
       mutate(variable = substr(variable, 1, 11)) %>%
       left_join(skater_shift_onice_all %>%
            select(season, Game_Id, Period, Home_Team, Away_Team, Shift_Start, ends_with("_elo")) %>%
            melt(id.vars = c("season", "Game_Id", "Period", "Home_Team", "Away_Team", "Shift_Start"), value.name = "elo") %>%
            mutate(variable = substr(variable, 1, 11)),
            by = c("season", "Game_Id", "Period", "Home_Team", "Away_Team", "Shift_Start","variable")) %>%
        na.omit() %>%
        mutate(variable = substr(variable, 1, 4)) %>%
        group_by(season, Game_Id, Period, Home_Team, Away_Team, Shift_Start, variable, pos) %>%
        summarise(pos_elo = mean(elo, na.rm = T)) %>%
        dcast(season + Game_Id + Period + Home_Team + Away_Team + Shift_Start ~ paste0(variable, "_elo_",pos), value.var = "pos_elo") %>%
      mutate(away_elo_D = zoo::na.locf(away_elo_D),
             away_elo_F = zoo::na.locf(away_elo_F),
             home_elo_D = zoo::na.locf(home_elo_D),
             home_elo_F = zoo::na.locf(home_elo_F))


skater_onice_data_clean <- skater_shift_onice_all %>%
       select(season, Game_Id, Period, Home_Team, Away_Team, Shift_Start, ends_with("_id")) %>%
       melt(id.vars = c("season", "Game_Id", "Period", "Home_Team", "Away_Team", "Shift_Start")) %>%
       mutate(variable2 = ifelse(substr(variable, 1, 4) == "home","Home_Strength",
                          ifelse(substr(variable, 1, 4) == "away","Away_Strength",NA))) %>%
      na.omit() %>%
      distinct() %>%
      group_by(season, Game_Id, Period, Home_Team, Away_Team, Shift_Start, variable2) %>%
      mutate(Strength = n_distinct(value)) %>%
      dcast(season + Game_Id + Period + Home_Team + Away_Team + Shift_Start ~ variable2, value.var = "Strength", fun.aggregate = mean) %>%
      mutate(Away_Strength = ifelse(Away_Strength < 3, NA, Away_Strength),
             Home_Strength = ifelse(Home_Strength < 3, NA, Home_Strength),
             Away_Strength = zoo::na.locf(Away_Strength),
             Home_Strength = zoo::na.locf(Home_Strength)) 


skater_onice_data_clean2 <- skater_shift_onice_all %>%
      left_join(skater_onice_pos_clean, by = c("season", "Game_Id", "Period", "Home_Team", "Away_Team", "Shift_Start")) %>%
      left_join(skater_onice_data_clean, by = c("season", "Game_Id", "Period", "Home_Team", "Away_Team", "Shift_Start")) %>%
      mutate(Home_Game_Strength = paste0(Home_Strength,"v",Away_Strength),
             Home_Game_State = ifelse(Home_Game_Strength %in% c("5v5","6v6","4v4","3v3"),"EV",
                                ifelse(Home_Game_Strength %in% c("6v3","6v4","5v3","6v5","5v4","4v3"),"PP",
                                ifelse(Home_Game_Strength %in% c("3v5","3v4","3v6","4v5","4v6","5v6","4v5","6v7"),"SH","Other")))) %>%
      filter(Home_Game_State != "Other") %>%
      arrange(season, Game_Id, Shift_Start) %>%
      group_by(season, Game_Id) %>%
      mutate(Home_Score = cumsum(ifelse((Home_Team == lag(Ev_Team)) & (lag(Event) %in% c("GOAL")), 1, 0)),
             Away_Score = cumsum(ifelse((Home_Team != lag(Ev_Team)) & (lag(Event) %in% c("GOAL")), 1, 0)))
  
test <- skater_onice_data_clean2 %>%
      filter(season == "20172018" & Game_Id == 20050) %>%
      select(ends_with("Team"), ends_with("Score"), Event, starts_with("Shift"))



#> dim(skater_onice_data_clean)
#[1] 2686199      60
#
game_states <- skater_onice_data_clean2 %>% 
        group_by(Home_Game_State, Home_Game_Strength) %>%
        summarise(cnt = n(),
                  duration = sum(Shift_Duration))


save(skater_onice_data_clean2, file="~/Documents/CWA/Hockey Data/skater_onice_data_clean.RData")


sm_gm_check <- skater_onice_data_clean2 %>%
    filter(season == "20172018" & Game_Id == 20050) %>%
    filter(awayPlayer1_id %in% c(i) | awayPlayer2_id %in% c(i) | awayPlayer3_id %in% c(i) | awayPlayer4_id %in% c(i) | awayPlayer5_id %in% c(i) | awayPlayer6_id %in% c(i) | homePlayer1_id %in% c(i) | homePlayer2_id %in% c(i) | homePlayer3_id %in% c(i) | homePlayer4_id %in% c(i) | homePlayer5_id %in% c(i) | homePlayer6_id %in% c(i) ) 
 
 

```

### Player Function

```{r}


skater_season_stats <- function(i,szns = c("20142015","20152016","20162017","20172018")) {
    
    player_name <- skater_id_list %>% filter(shooterID == i) %>% ungroup() %>% select(Player) %>% distinct() %>% as.character()
    player_quality <- player_level_quality %>% filter(shooterID == i) %>% select(season, Pos, Predicted_CS) %>% rename(csScore = Predicted_CS)
    
    print(player_name)

    ### Player On-Ice For Events
    player_onice <- tryCatch(skater_onice_data_clean2 %>%
          filter(season %in% szns) %>%
          filter(awayPlayer1_id %in% c(i) | awayPlayer2_id %in% c(i) | awayPlayer3_id %in% c(i) | awayPlayer4_id %in% c(i) | awayPlayer5_id %in% c(i) | awayPlayer6_id %in% c(i) | homePlayer1_id %in% c(i) | homePlayer2_id %in% c(i) | homePlayer3_id %in% c(i) | homePlayer4_id %in% c(i) | homePlayer5_id %in% c(i) | homePlayer6_id %in% c(i) ) %>%
         
          mutate(Player = as.factor(player_name),
                 Player_Id = i,
                 Team = ifelse(awayPlayer1_id %in% c(i) | awayPlayer2_id %in% c(i) | awayPlayer3_id %in% c(i) | awayPlayer4_id %in% c(i) | awayPlayer5_id %in% c(i) | awayPlayer6_id %in% c(i), Away_Team, Home_Team),
                  Player_State = ifelse(Team == Home_Team | Home_Game_State == "EV",Home_Game_State,
                         ifelse(Home_Game_State == "SH" & Team != Home_Team,"PP",
                         ifelse(Home_Game_State == "PP" & Team != Home_Team,"SH",
                                "EV"))))) %>%
            left_join(player_quality, by = "season")

      ### Player Shift Sums
      player_shifts_data_raw <- tryCatch(shift_all_raw %>%
            filter(season %in% szns) %>%
            filter(Player_Id == i) %>%
            mutate(shift_bool = 1,
                   season = as.integer(as.character(season)),
                   Player = as.factor(player_name)) %>%
            group_by(season, Player, Player_Id, Game_Id) %>% 
            mutate(Game_Shift_No = cumsum(shift_bool)) %>%
            group_by(season, Player, Player_Id) %>% 
            mutate(Season_Shift_No = cumsum(shift_bool),
                   Start = ((Period - 1) * 1200 ) + Start,
                   End = ((Period - 1) * 1200 ) + End
            ))
                   
      

        ### Leaves out shifts with no events
        player_shifts_data <- sqldf::sqldf("
                      SELECT Start,End,Duration, shift_bool,Game_Shift_No,Season_Shift_No, b.*
                      FROM player_shifts_data_raw as a
                      INNER JOIN player_onice as b
                      ON a.Player = b.Player
                      AND a.Player_Id = b.Player_Id
                      AND a.season = b.season
                      AND a.Game_Id = b.Game_Id
                      AND a.Period = b.Period
                      AND a.start < Shift_Start
                      AND a.end >= Shift_Start
                  ") %>%
              #group_by(Player, Player_Id, season, Game_Id) %>%
              mutate(Player_State = ifelse(Home_Game_Strength %in% c("5v5","6v6","4v4","3v3"),"EV",
                                ifelse((Team == Home_Team) & Home_Game_Strength %in% c("6v3","6v4","5v3","6v5","5v4","4v3"),"PP",
                                ifelse((Team != Home_Team) & Home_Game_Strength %in% c("6v3","6v4","5v3","6v5","5v4","4v3"),"SH",
                                ifelse((Team == Home_Team) & Home_Game_Strength %in% c("3v5","3v4","3v6","4v5","4v6","5v6","4v5","6v7"),"SH",
                                ifelse((Team != Home_Team) & Home_Game_Strength %in% c("3v5","3v4","3v6","4v5","4v6","5v6","4v5","6v7"),"PP",
                                
                                "Other"))))),
                     
                     SF = ifelse((Team == Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), 1, 0),
                     SA = ifelse((Team != Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), 1, 0),
                     GF = ifelse((Team == Ev_Team) & (Event %in% c("GOAL")), 1, 0),
                     GA = ifelse((Team != Ev_Team) & (Event %in% c("GOAL")), 1, 0),
                     xGF = ifelse((Team == Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), xG_team, 0),
                     xGA = ifelse((Team != Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), xG_team, 0),
                     
                     G = ifelse(Event == "GOAL" & p1_ID %in% c(i), 1, 0),
                     A1 = ifelse(Event == "GOAL" & p2_ID %in% c(i), 1, 0),
                     A2 = ifelse(Event == "GOAL" & p3_ID %in% c(i), 1, 0),
                     ixG = ifelse(p1_ID %in% c(i), xG, 0),
                     iSF = ifelse(p1_ID %in% c(i), SF, 0),
   
                     PenDraw = ifelse((Team != Ev_Team) & (Event %in% c("PENL")), 1, 0),
                     PenTake = ifelse((Team == Ev_Team) & (Event %in% c("PENL")), 1, 0),
                     
                     iPenDraw = ifelse((Team != Ev_Team) & Event %in% c("PENL") & (p1_ID %in% c(i) | p2_ID %in% c(i)), 1, 0),
                     iPenTake = ifelse((Team == Ev_Team) & Event %in% c("PENL") & (p1_ID %in% c(i) | p2_ID %in% c(i)), 1, 0),
                    
                     ZoneStart = ifelse(Shift_Start != Start,"OTF",
                                 ifelse(Home_Zone == "Neu","Neu",
                                 ifelse(Team == Home_Team, as.character(Home_Zone),
                                 ifelse(Home_Zone == "Def","Off","Def")))),
                     
                     Team_Score = ifelse(Team == Home_Team, Home_Score, Away_Score),
                     Opp_Score = ifelse(Team == Home_Team, Away_Score, Home_Score),
                     
                     Score_State = ifelse(Team_Score == Opp_Score,"Tied",
                                   ifelse(abs(Team_Score - Opp_Score) < 4,as.character(Team_Score - Opp_Score),
                                   ifelse(Team_Score - Opp_Score > 3,"Up3+",
                                                "Down3+"))),
                     
                  ## Adjust Quality
                  away_elo_D = ifelse(Pos == "D" & Team != Home_Team, ((away_elo_D * Away_Strength) - csScore) / (Away_Strength - 1), away_elo_D),
                  away_elo_F = ifelse(Pos == "F" & Team != Home_Team, ((away_elo_F * Away_Strength) - csScore) / (Away_Strength - 1), away_elo_F),
                  
                  home_elo_D = ifelse(Pos == "D" & Team == Home_Team, ((home_elo_D * Home_Strength) - csScore) / (Home_Strength - 1), home_elo_D),
                  home_elo_F = ifelse(Pos == "F" & Team == Home_Team, ((home_elo_F * Home_Strength) - csScore) / (Home_Strength - 1), home_elo_F),
                  
                 Mean_Teammates_F = ifelse(Team == Home_Team, home_elo_F, away_elo_F),
                 Mean_Teammates_D = ifelse(Team == Home_Team, home_elo_D, away_elo_D),
                 
                 Mean_Competition_F = ifelse(Team != Home_Team, home_elo_F, away_elo_F),
                 Mean_Competition_D = ifelse(Team != Home_Team, home_elo_D, away_elo_D),

                 Mean_Teammates_F = ifelse(Mean_Teammates_F < 101 & Mean_Teammates_F >= 0, Mean_Teammates_F, NA),
                 Mean_Teammates_D = ifelse(Mean_Teammates_D < 101 & Mean_Teammates_D >= 0, Mean_Teammates_D, NA),
                 
                 Mean_Competition_F = ifelse(Mean_Competition_F < 101 & Mean_Competition_F >= 0, Mean_Competition_F, NA),
                 Mean_Competition_D = ifelse(Mean_Competition_D < 101 & Mean_Competition_D >= 0, Mean_Competition_D, NA),

                 shift_event_index = cumsum(shift_bool),
                 FO_Shift = max(ifelse(Start == Shift_Start & Event == "FAC",1,0)),
                
                 #OTF_Shift = ifelse((Seconds_Elapsed - lag(Seconds_Elapsed)) != TOI & FO_Shift != 1, 1, 0),
                 Player_Venue = ifelse(Team == Home_Team, "Home","Away"),
                 OTF_Shift =  max(ifelse(Start != Shift_Start & shift_event_index == 1, 1, 0)),
    
                 Off_FO_Shift = max(ifelse(FO_Shift == 1 & shift_event_index == 1 & ((Player_Venue == "Home" & Home_Zone == "Off") | (Player_Venue == "Away" & Home_Zone == "Def")),1,0)),
                 Def_FO_Shift = max(ifelse(FO_Shift == 1 & shift_event_index == 1 & ((Player_Venue == "Home" & Home_Zone == "Def") | (Player_Venue == "Away" & Home_Zone == "Off")),1,0)),
                 Neu_FO_Shift = max(ifelse(FO_Shift == 1 & shift_event_index == 1 & Home_Zone == "Neu",1,0))) 
        
        

      season_bystrength_game <- player_shifts_data %>%
          group_by(Player, Player_Id, season, Player_State, Game_Id) %>%
          summarise(                
                Shifts = n_distinct(Season_Shift_No),

                ixG = sum(ixG, na.rm = TRUE),
                Goals = sum(G, na.rm = TRUE),
                Primary_Points  = sum(G, na.rm = TRUE) + sum(A1, na.rm = TRUE),
                Points = sum(G, na.rm = TRUE) + sum(A1, na.rm = TRUE) + sum(A2, na.rm = TRUE),
                
                GF = sum(GF, na.rm = TRUE),
                GA = sum(GA, na.rm = TRUE),
                
                xGF = sum(xGF, na.rm = TRUE),
                xGA = sum(xGA, na.rm = TRUE),
                SF = sum(SF, na.rm = TRUE),
                SA = sum(SA, na.rm = TRUE),
                
                iSF = sum(iSF, na.rm = TRUE),

                iPenalty_Drawn = sum(iPenDraw, na.rm = T),
                iPenalty_Taken = sum(iPenTake, na.rm = T),
            
                Penalty_Drawn = sum(PenDraw, na.rm = T),
                Penalty_Taken = sum(PenTake, na.rm = T),
            
                Mean_Teammates_F = weighted.mean(Mean_Teammates_F, w = Shift_Duration),
                Mean_Teammates_D = weighted.mean(Mean_Teammates_D, w = Shift_Duration),
                Mean_Competition_F = weighted.mean(Mean_Competition_F, w = Shift_Duration),
                Mean_Competition_D = weighted.mean(Mean_Competition_D, w = Shift_Duration),
                
                TOI = sum(Shift_Duration) / 60
                
                ) 
      
          return(season_bystrength_game)

}


sm_results <- skater_season_stats(8477497)

```

## Season Data

```{r echo=FALSE, results="hide"}

skater_list1417 <- skater_id_list %>% filter(season %in% c("20142015","20152016","20162017")) %>% select(shooterID) %>% unique() 

skater_game_stats_1417 <- plyr::rbind.fill(lapply(FUN=skater_season_stats,skater_list1417$shooterID,szns = c("20142015","20152016","20162017")))

save(skater_game_stats_1417, file="~/Documents/CWA/Hockey Data/skater_game_stats_1417.RData")

skater_list_18 <- skater_id_list %>% filter(season %in% c("20172018")) %>% select(shooterID) %>% unique() 

skater_game_stats_18 <- plyr::rbind.fill(lapply(FUN=skater_season_stats,skater_list_18$shooterID,szns = c("20172018")))

save(skater_game_stats_18, file="~/Documents/CWA/Hockey Data/skater_game_stats_18.RData")

print("Done")
```

### Join CrowdScout Score, Break Season into Chunks

```{r}
load("~/Documents/CWA/Hockey Data/skater_game_stats_1417.RData")
load("~/Documents/CWA/Hockey Data/skater_game_stats_18.RData")

min_chunk_games <- 20

skater_game_stats <- skater_game_stats_1417 %>%
          bind_rows(skater_game_stats_18) %>%
          filter(Player_State != "PS")

skater_stats_chunked <- function(seed) {
  
  set.seed(seed)

  skater_gamechunk_grouped <- skater_game_stats %>%
            group_by(Player, Player_Id, season) %>%
            mutate(Season_Gm_Cnt = n_distinct(Game_Id),
                   Player_Chunks = ceiling(Season_Gm_Cnt / min_chunk_games),
                   Game_Chunk = ceiling(runif(n(), 0,Player_Chunks))) %>%
            filter(Season_Gm_Cnt >= 10) %>%
            group_by(Player, Player_Id, season, Game_Chunk) %>%
            mutate(Sample_Games = n_distinct(Game_Id)) %>%
            select(-c(Game_Id)) %>%
            group_by(Player, Player_Id, season, Game_Chunk, Player_State, Sample_Games) 

  skater_gamechunk_qualcomp <- skater_gamechunk_grouped %>%
            summarise(Mean_Competition_D = weighted.mean(Mean_Competition_D, w=TOI, na.rm = TRUE),
                      Mean_Competition_F = weighted.mean(Mean_Competition_F, w=TOI, na.rm = TRUE),
                      
                      Mean_Teammates_D = weighted.mean(Mean_Teammates_D, w=TOI, na.rm = TRUE),
                      Mean_Teammates_F = weighted.mean(Mean_Teammates_F, w=TOI, na.rm = TRUE)
                      )
          
  skater_gamechunk_sums <- skater_gamechunk_grouped %>%
            summarise_at(vars(ends_with("Goals"),
                              ends_with("Drawn"),
                              ends_with("Taken"),
                              ends_with("SF"),
                              ends_with("SA"),
                              ends_with("ixG"),
                              ends_with("Points"),
                              ends_with("Shifts"),
                              ends_with("GF"),
                              ends_with("GA"),
                               ends_with("TOI")
                              ), sum, na.rm = TRUE) %>%
            left_join(skater_gamechunk_qualcomp, by = c("Player", "Player_Id", "season", "Game_Chunk","Player_State","Sample_Games")) %>%
            melt(id.vars = c("Player", "Player_Id", "season", "Game_Chunk","Player_State","Sample_Games")) %>%
            mutate(iteration = seed)

    return(skater_gamechunk_sums)
}    


skater_gamechunk_stats <- do.call(dplyr::bind_rows,lapply(FUN=skater_stats_chunked,c(1:10)))

```

### Function to calculate differentials

```{r}
load("~/Documents/CWA/Hockey Data/player_onice_data_clean.RData")

### Calculate strength rates
strength_df <- player_onice_data_clean %>%
                    filter(Home_Game_State != "PS") %>%
                    filter(!is.na(Ev_Team)) %>%
                    mutate(Home_Sample = ifelse(Ev_Team == Home_Team, 1, 0),
                            PenDraw = ifelse((Home_Team != Ev_Team) & (Event %in% c("PENL")), 1, 0),
                            PenTake = ifelse((Home_Team == Ev_Team) & (Event %in% c("PENL")), 1, 0),
                            SF = ifelse((Home_Team == Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), 1, 0),
                            SA = ifelse((Home_Team != Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), 1, 0),
                            GF = ifelse((Home_Team == Ev_Team) & (Event %in% c("GOAL")), 1, 0),
                            GA = ifelse((Home_Team != Ev_Team) & (Event %in% c("GOAL")), 1, 0),
                            xGF = ifelse((Home_Team == Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), xG_team, 0),
                            xGA = ifelse((Home_Team != Ev_Team) & (Event %in% c("SHOT","MISS","BLOCK","GOAL")), xG_team, 0))

strength_df2 <- strength_df %>%
                    group_by(Home_Sample) %>%
                    sample_n(size = sum(strength_df$Home_Sample), `replace` = TRUE)

strength_rates <- strength_df2 %>%
                    group_by(Home_Game_State) %>%
                    summarise(S_Baseline = sum(SF) / (sum(SF) + sum(SA)),
                              Pen_Baseline = sum(PenDraw) / (sum(PenDraw) + sum(PenTake)),
                              G_Baseline = sum(GF) / (sum(GF) + sum(GA)),
                              xG_Baseline = sum(xGF) / (sum(xGF) + sum(xGA))
                              ) %>%
                    melt() %>%
                    dcast(variable ~ Home_Game_State) %>%
                    mutate(PP = PP / (EV / 0.5),
                           SH = SH / (EV / 0.5),
                           EV = 0.5) %>%
                    melt(variable.name = "Player_State") %>%
                    dcast(Player_State ~ variable)

load("~/Documents/CWA/Hockey Data/player_level_quality.RData")

skater_production_baseline <- skater_game_stats %>%
        left_join(player_level_quality %>% select(shooterID, Pos) %>% rename(Player_Id = shooterID) %>% distinct(), by = c("Player_Id")) %>%
        filter(!is.na(Pos)) %>%
        group_by(Player_State, Pos) %>%
        summarise(mean_pos_ixG60 = sum(ixG) / (sum(TOI) / 60),
                  mean_pos_G60 = sum(Goals) / (sum(TOI) / 60),
                  mean_pos_Primary_Points60 = sum(Primary_Points) / (sum(TOI) / 60),
                  mean_pos_Points60 = sum(Points) / (sum(TOI) / 60),
                  mean_pos_TOI = mean(TOI),
                  mean_pos_iPenDrawn = sum(iPenalty_Drawn) / (sum(TOI) / 60),
                  mean_pos_iPenTaken = sum(iPenalty_Taken) / (sum(TOI) / 60)
                  )


```

### Create regressed metrics

```{r}

## Beta Functions
calcBetaMode <- function(aa, bb) { BetaMode <- (aa - 1)/(aa + bb - 2); return(BetaMode); }
calcBetaMean <- function(aa, bb) { BetaMean <- (aa)/(aa + bb); return(BetaMean); }
calcBetaSd   <- function(aa, bb) { BetaSd <- sqrt((aa * bb)/(((aa + bb)^2) * (aa + bb + 1))); return(BetaSd); }


beta_lift_fun <- function(for_metric, against_metric, TOI, strength_rate, prior = 2000, type = "POST") {
  
      
      beta_a = prior * strength_rate
      beta_b = prior * (1-strength_rate) #(for_metric + against_metric) - beta_a
      
      # Overall
      likelihood_a = for_metric + 1  ## Saves + 1
      likelihood_b = against_metric + 1  ## Goals + 1
      
      posterior_a = beta_a + (likelihood_a - 1)  ## Success + Beta A
      posterior_b = beta_b +  (likelihood_b - 1)  ## Goals + Beta B

      prior_mean      = calcBetaMean(beta_a, beta_b)
      posterior_mean  = calcBetaMean(posterior_a, posterior_b)

      if(type == "POST") {
          out  = calcBetaMean(posterior_a, posterior_b) - calcBetaMean(beta_a, beta_b)
        } else {
          out = calcBetaMean(beta_a, beta_b)
        }

      return(out)
}

kr21_regressor <- function(player_value, player_toi, mean_rate, mean_toi, sample_games) {

   ## Per game stabilizer
    total_TOI_over_sample <- mean_toi * sample_games * 0.5
    
    out <- (((player_value * player_toi) + (total_TOI_over_sample * mean_rate)) / (player_toi + total_TOI_over_sample))
    
    return(out)
}

#kr21_regressor(0.6, 200, 0.5, 15, 40)


shots_game <- 30
shooting_pct <- 0.04804833
pen_shot_ratio <- 0.06903094


skater_gamechunk_stats2 <- skater_gamechunk_stats %>%
   dcast(Player + Player_Id + season + iteration + Game_Chunk + Sample_Games + Player_State ~ variable) %>%
            left_join(strength_rates, by = "Player_State") %>%
            left_join(player_level_quality %>% select(shooterID, Pos) %>% rename(Player_Id = shooterID) %>% distinct(), by = c("Player_Id")) %>%
            left_join(skater_production_baseline, by = c("Player_State","Pos")) %>%
            mutate(regressed_SF_Share = beta_lift_fun(SF, SA, TOI, S_Baseline, Sample_Games * shots_game, "POST"),
                   regressed_GF_Share = beta_lift_fun(GF, GA, TOI, G_Baseline, Sample_Games * shots_game * shooting_pct, "POST"),
                   regressed_xGF_Share = beta_lift_fun(xGF, xGA, TOI, xG_Baseline, Sample_Games * shots_game * shooting_pct, "POST"),
                   regressed_iPen_Share = beta_lift_fun(iPenalty_Drawn, iPenalty_Taken, TOI, Pen_Baseline, Sample_Games * shots_game * pen_shot_ratio, "POST"),
                  regressed_ixG60 = kr21_regressor(ixG, TOI, mean_pos_ixG60, mean_pos_TOI, Sample_Games),
                  regressed_G60 = kr21_regressor(Goals, TOI, mean_pos_G60, mean_pos_TOI, Sample_Games),
                  regressed_Primary_Points60 = kr21_regressor(Primary_Points, TOI, mean_pos_Primary_Points60, mean_pos_TOI, Sample_Games),
                  regressed_Points60 = kr21_regressor(Points, TOI, mean_pos_Points60, mean_pos_TOI, Sample_Games),
                  regressed_iPenDrawn60 = kr21_regressor(iPenalty_Drawn, TOI, mean_pos_iPenDrawn, mean_pos_TOI, Sample_Games),
                  regressed_iPenTaken60 = kr21_regressor(iPenalty_Taken, TOI, mean_pos_iPenTaken, mean_pos_TOI, Sample_Games),
                  TOI_Gm = TOI / Sample_Games
                   ) %>%
      select(c(Player,Player_Id,season,iteration,Game_Chunk,Sample_Games,Player_State),
             starts_with("regressed"),
             starts_with("TOI_Gm"),
             starts_with("Mean"),
             -starts_with("mean_pos")
             ) %>%
        melt(id.vars = c("Player","Player_Id","season","iteration","Game_Chunk","Sample_Games","Player_State")) %>%
        mutate(variable = paste0(variable,"_",Player_State)) %>%
        dcast(Player + Player_Id + season + iteration + Game_Chunk + Sample_Games ~ variable) %>%
        mutate_if(is.numeric, funs(replace(., is.na(.), 0)))
       
            
            
          
colnames(skater_gamechunk_stats2)

head(skater_gamechunk_stats2$TOI_EV)
```


## Crowdscout Training Data

```{r}

conn <- RMySQL::dbConnect(RMySQL::MySQL(), user='ca_elo_games', password='cprice31!',
                  host='mysql.crowdscoutsports.com', db='nhl_all')
on.exit(dbDisconnect(conn))

player_season_elo <- dbGetQuery(conn, "SELECT ID as Player_Id,
                         CASE WHEN Date <= '2016-10-01' THEN 20152016
                              WHEN Date <= '2017-10-01' THEN 20162017
                              WHEN Date <= '2018-10-01' THEN 20172018
                              WHEN Date <= '2019-10-01' THEN 20182019
                              WHEN Date <= '2020-10-01' THEN 20192020
                              WHEN Date <= '2021-10-01' THEN 20202021 
                              WHEN Date <= '2022-10-01' THEN 20212022 END AS season, avg(score) as Score
                         FROM hockey_daily_elo_py AS A
                         WHERE Date >= '2015-10-01'
                         GROUP BY 1,2")

player_season_last_elo <- dbGetQuery(conn, "SELECT ID as Player_Id,
                         CASE WHEN Date <= '2016-10-01' THEN 20152016
                              WHEN Date <= '2017-10-01' THEN 20162017
                              WHEN Date <= '2018-10-01' THEN 20172018
                              WHEN Date <= '2019-10-01' THEN 20182019
                              WHEN Date <= '2020-10-01' THEN 20192020
                              WHEN Date <= '2021-10-01' THEN 20202021 
                              WHEN Date <= '2022-10-01' THEN 20212022 END AS season, cron_ts, score as Last_Score
                         FROM hockey_daily_elo_py AS A
                         WHERE Date >= '2015-10-01'
                         GROUP BY 1,2
                         HAVING max(cron_ts) OR cron_ts IS NULL") %>% select(-c(cron_ts))


load("~/Documents/CWA/Hockey Data/player_level_quality.RData")

skater_gamechunk_stats_elo <- skater_gamechunk_stats2 %>%
        filter(season != "20142015") %>%
        mutate(season = as.integer(season)) %>%
        inner_join(player_season_elo, by = c("Player_Id", "season")) %>%
        inner_join(player_season_last_elo, by = c("Player_Id", "season")) %>%
        left_join(player_level_quality %>% select(shooterID, Pos) %>% rename(Player_Id = shooterID) %>% distinct(), by = c("Player_Id")) %>%
        na.omit()

dim(skater_gamechunk_stats2 %>% filter(season != "20142015"))
dim(skater_gamechunk_stats_elo) ## 49650

```
### Model Player Score

```{r}
library(xgboost); library(caret)
model_features <- skater_gamechunk_stats_elo %>% select(-c(Player,Player_Id,season,iteration,Game_Chunk,Sample_Games, Pos), ends_with("Score"))

preProcValues <- caret::preProcess(model_features, method = c("center", "scale"))
model_data <- predict(preProcValues, model_features) %>%
        mutate(Pos_F = ifelse(skater_gamechunk_stats_elo$Pos == "F",1,0))

dim(model_data)

lm_model <- glm(skater_gamechunk_stats_elo$Score ~ . , data = model_data)

index <- createDataPartition(skater_gamechunk_stats_elo$Pos, p=0.75, list=FALSE)
train_data <- xgb.DMatrix(as.matrix(model_data),label=skater_gamechunk_stats_elo[,c("Last_Score")] )
test_data <- xgb.DMatrix(as.matrix(model_data[-index,]),label=skater_gamechunk_stats_elo[-index,c("Last_Score")] )
model_dbg <- xgb.DMatrix(as.matrix(model_data[,]),label=skater_gamechunk_stats_elo[,c("Last_Score")] )

bst_model <- xgb.train( params = list(objective = "reg:linear",
            eta = 0.05,   # step size / shrinkage
            max_depth = 6,  # Max depth of each tree
            gamma = 0,    # Minimum loss function for leaf to be split
            min_child_weight = 20,    # Min number of cases in leaf
            subsample = 0.3,    # Sample of cases for each tree
            colsample_bytree = 0.7,  # Ratio of columns to sample
            missing = NA,
            stratified = TRUE,
            nthread = 2,   # maximum number of cores/ threads to use for training
            early_stopping_rounds = 5,  # set to value of consecutive worse performance to terminate
            nfold = 5,
            base_score = mean(skater_gamechunk_stats_elo$Last_Score),
            prediction = TRUE,
            verbose = 1, 
            print_every_n = 25,
            metrics = "rmse"),
            train_data, nrounds = 100, list(eval = test_data, train = train_data))

importance_matrix <- xgb.importance(feature_names = colnames(model_data), model = bst_model)
importance_plot = xgb.plot.importance(importance_matrix)

importance_plot

## Output predicted values
predicted <- predict(bst_model, model_dbg,type="prob")

```

### Predicted Player Scores

```{r}

player_running_scores <- function(i) {

  skater_games <- skater_game_stats %>%
            filter(Player_Id == i) 

  skater_games2 <- skater_games %>% select(season,Game_Id) %>% distinct() %>% mutate(game_index = row_number()) %>%
            left_join(skater_games, by = c("season","Game_Id"))

  running10_sums <- function(index) {
      
    game_10 <- skater_games2 %>%
          filter((game_index >= (index - 10)) & (game_index <= index))
    
    game_10_qualcomp <- game_10 %>%
            group_by(Player, Player_Id, Player_State) %>%
            summarise(season = max(season),
                      Game_Index = max(index),
                      Mean_Competition_D = weighted.mean(Mean_Competition_D, w=TOI, na.rm = TRUE),
                      Mean_Competition_F = weighted.mean(Mean_Competition_F, w=TOI, na.rm = TRUE),
                      
                      Mean_Teammates_D = weighted.mean(Mean_Teammates_D, w=TOI, na.rm = TRUE),
                      Mean_Teammates_F = weighted.mean(Mean_Teammates_F, w=TOI, na.rm = TRUE)
                      )

      game_10_sums <- game_10 %>%
            group_by(Player, Player_Id, Player_State) %>%
            summarise_at(vars(ends_with("Goals"),
                              ends_with("Drawn"),
                              ends_with("Taken"),
                              ends_with("SF"),
                              ends_with("SA"),
                              ends_with("ixG"),
                              ends_with("Points"),
                              ends_with("Shifts"),
                              ends_with("GF"),
                              ends_with("GA"),
                               ends_with("TOI")
                              ), sum, na.rm = TRUE) %>%
            left_join(game_10_qualcomp, by = c("Player", "Player_Id","Player_State")) %>%
            filter(TOI > 0)
      
        return(game_10_sums)

  }
  
  game_indices <- 10:max(skater_games2$game_index)

  skater_rolling_average <- do.call(dplyr::bind_rows,lapply(FUN=running10_sums,game_indices))

  return(skater_rolling_average)
  
}  



player_ids <- unique(skater_game_stats$Player_Id)

skater_rolling_averages <- do.call(dplyr::bind_rows,lapply(FUN=player_running_scores,player_ids))

save(skater_rolling_averages, file="~/Documents/CWA/Hockey Data/skater_rolling_averages.RData")

```



```{r}
load("~/Documents/CWA/Hockey Data/skater_rolling_averages.RData")

skater_rolling_average2 <- skater_rolling_averages %>%
            left_join(strength_rates, by = "Player_State") %>%
            left_join(player_level_quality %>% select(shooterID, Pos) %>% rename(Player_Id = shooterID) %>% distinct(), by = c("Player_Id")) %>%
            left_join(skater_production_baseline, by = c("Player_State","Pos")) %>%
            mutate(regressed_SF_Share = beta_lift_fun(SF, SA, TOI, S_Baseline, 10 * shots_game, "POST"),
                   regressed_GF_Share = beta_lift_fun(GF, GA, TOI, G_Baseline, 10 * shots_game * shooting_pct, "POST"),
                   regressed_xGF_Share = beta_lift_fun(xGF, xGA, TOI, xG_Baseline, 10 * shots_game * shooting_pct, "POST"),
                   regressed_iPen_Share = beta_lift_fun(iPenalty_Drawn, iPenalty_Taken, TOI, Pen_Baseline, 10 * shots_game * pen_shot_ratio, "POST"),
                  regressed_ixG60 = kr21_regressor(ixG, TOI, mean_pos_ixG60, mean_pos_TOI, 10),
                  regressed_G60 = kr21_regressor(Goals, TOI, mean_pos_G60, mean_pos_TOI, 10),
                  regressed_Primary_Points60 = kr21_regressor(Primary_Points, TOI, mean_pos_Primary_Points60, mean_pos_TOI, 10),
                  regressed_Points60 = kr21_regressor(Points, TOI, mean_pos_Points60, mean_pos_TOI, 10),
                  regressed_iPenDrawn60 = kr21_regressor(iPenalty_Drawn, TOI, mean_pos_iPenDrawn, mean_pos_TOI, 10),
                  regressed_iPenTaken60 = kr21_regressor(iPenalty_Taken, TOI, mean_pos_iPenTaken, mean_pos_TOI, 10),
                  TOI_Gm = TOI / 10
                   ) %>%
      select(c(Player,Player_Id,season,Player_State,Game_Index,Pos),
             starts_with("regressed"),
             starts_with("TOI_Gm"),
             starts_with("Mean"),
             -starts_with("mean_pos")
             ) %>%
        melt(id.vars = c("Player","Player_Id","season","Pos","Player_State","Game_Index")) %>%
        mutate(variable = paste0(variable,"_",Player_State)) %>%
        dcast(Player + Player_Id + season + Pos + Game_Index ~ variable) %>%
        mutate_if(is.numeric, funs(replace(., is.na(.), 0))) 
  
preProcRolling <- caret::preProcess(skater_rolling_average2, method = c("center", "scale"))
skater_rolling_data <- predict(preProcRolling, skater_rolling_average2) %>%
        mutate(Pos_F = ifelse(skater_rolling_average2$Pos == "F",1,0))

predicted <- predict(bst_model,xgb.DMatrix(data.matrix(skater_rolling_data)),type="prob")


skater_rolling_average_scores <- skater_rolling_average2 %>%
        mutate(Predicted_Score = predict(lm_model, skater_rolling_data))  #predicted)


ggplot(data = skater_rolling_average_scores, aes(x=predicted)) +
    geom_density()

colnames(model_features)

skater_rolling_average_scores100 <- skater_rolling_average_scores %>%
      arrange(-Predicted_Score) %>%
      head(100)

```

### Plot 

```{r}

i = 8471675

skater_rolling_average_scores100 <- skater_rolling_average_scores %>%
      arrange(-Predicted_Score) %>%
      head(100)


rolling_game_plot <- skater_rolling_average_scores %>%
      filter(Player_Id == i) %>%
      ggplot(aes(x=Game_Index, y = Predicted_Score, color=as.factor(season))) +
      geom_line() +
      labs(title = "10-Game Rolling Average",
           x="Game",
           y="Estimated Ability (Scaled 0 - 100)") +
      ylim(0,100)

ggsave(filename=paste0("/Users/colander1/Downloads/rolling_game_plot.png"), plot=rolling_game_plot,  width=18, height=12)



team_toi <- feather::read_feather("/Users/colander1/anaconda3/lib/python3.6/site-packages/scrapenhl2/data/teams/toi/2017/BOS.feather")

```